### 2019-01-21 museum.tex
removed parametricity

>>>>

\subsection{Parametricity}

To be filled in much later\ldots

\begin{definition}\label{def_param_candidate}\normalfont
  For two type constructors~$\tau_1,\tau_2$ of the same kind~$\kappa$,
  we define by induction on~$\kappa$ the set~$\Rel_{\tau_1,\tau_2}$ of
  $\tau_1,\tau_2$-candidates.

  Assume $\kappa=*$, i.e., $\tau_1,\tau_2$ are types. A relation~$R$
  between terms of type~$\tau_1$ and terms of type~$\tau_2$ is a
  \emph{candidate relation} in $\Rel_{\tau_1,\tau_2}$ when the
  following properties are satisfied:
  \begin{enumerate}
  \item if $R(t_1,t_2)$ and $t_1' \leadsto t_1$ (resp.~$t_2' \leadsto
    t_2$) then $R(t_1',t_2)$ (resp.~$R(t_1,t_2')$),
  \item \ldots
  \end{enumerate}
\end{definition}

\begin{lemma}\label{lem_beta_param_candidate}
  If $\sigma_1 =_\beta \sigma_1'$ and $\sigma_2 =_\beta \sigma_2'$
  then $\Rel_{\sigma_1,\sigma_2} = \Rel_{\sigma_1',\sigma_2'}$.
\end{lemma}

\begin{proof}
  Induction on the kind of~$\sigma_1,\sigma_2$.
\end{proof}

\begin{definition}\label{def_param_valuation}\normalfont
  Let $\omega$ be a mapping from type constructor variables to pairs
  of type constructors (respecting kinds). The mapping~$\omega$
  extends in an obvious way to a mapping from type constructors to
  pairs type constructors. We write $\omega_i(\tau)$ for the $i$-th
  component of the pair~$\omega(\tau)$. A mapping~$\omega$ is
  \emph{closed for~$\sigma$} if $\omega_i(\alpha)$ is closed for
  $\alpha \in \FV(\sigma)$ (then $\omega_i(\sigma)$ is closed), for
  $i=1,2$.

  An \emph{$\omega$-valuation} is a mapping~$\xi$ on type constructor
  variables such that $\xi(\alpha) \in
  \Rel_{\omega_1(\alpha),\omega_2(\alpha)}$.

  For each type constructor~$\sigma$, each mapping~$\omega$ closed
  for~$\sigma$, and each $\omega$-valuation~$\xi$, we define
  $\rval{\sigma}{\xi}{\omega}$ by induction on~$\sigma$:
  \begin{itemize}
  \item $\rval{\alpha}{\xi}{\omega} = \xi(\alpha)$ for a type
    constructor variable~$\alpha$,
  \item $\rval{\nat}{\xi}{\omega}(t_1,t_2)$ iff $t_1 \approx_\nat t_2$,
  \item $\rval{\sigma \arrtype \tau}{\xi}{\omega}(t_1,t_2)$ iff $t_i :
    \omega_i(\sigma\arrtype\tau)$ and for all $s_1,s_2$ such that
    $\rval{\sigma}{\xi}{\omega}(s_1,s_2)$ we have
    $\rval{\tau}{\xi}{\omega}(t_1 s_1, t_2 s_2)$,
  \item $\rval{\forall(\alpha:\kappa)[\sigma]}{\xi}{\omega}(t_1,t_2)$
    iff $t_i : \omega_i(\forall\alpha\sigma)$ and for all closed type
    constructors~$\tau_1,\tau_2$ of kind~$\kappa$ and every $R \in
    \Rel_{\tau_1,\tau_2}$ we have
    $\rval{\sigma}{\xi[\subst{\alpha}{R}]}{\omega[\subst{\alpha}{(\tau_1,\tau_2)}]}$.
  \end{itemize}
\end{definition}
